SunPy - Python for Solar Physics

### 2014-01-29 authors.tex

\author{
% People who have directly contributed to the text, still in no order.
Stuart J. Mumford$^1$,
Steven Christe$^2$,
David P\'erez-Su\'arez$^3$,
Andrew R. Inglis$^{2,5}$,
Jack Ireland$^{6}$,
Albert Y. Shih$^2$,
Simon Liedtke$^{11}$,
Russell J. Hewett$^8$, %88
% Contributors to SunPy Sorted thus:
% No. Commits to main repo + commits in open PR's
% Date of most recent contribution
Florian Mayer$^{12}$, %721
Keith Hughitt, %446
Nabil Freij$^1$, %52
Matthew Earnshaw, %52
Tomas Meszaros$^{10}$, %17
N. Chorley, %17
Samuel M. Bennett$^1$, %14
M. Malocha, %10
J. Evans, %10
A. Maverick, %8
M. Bates, %6
Andrew J. Leonard$^7$, %3
J. Ballew, %3
Thomas P. Robitaille, %2
B. Mampaey, %2
%Hypnus1803 %1
and 
A. Kustov %1
}

@@

$^{12}$ Vienna University of Technology, Karlsplatz 13, 1040 Vienna, Austria
}

>>>>

\author{
% People who have directly contributed to the text, still in no order.
Stuart J Mumford$^1$,
Steven Christe$^2$,
David P\'erez-Su\'arez$^3$,
Andrew R Inglis$^{2,5}$,
Jack Ireland$^{6}$,
Albert Y Shih$^2$,
Simon Liedtke$^{11}$,
Russell J Hewett$^8$, %88
% Contributors to SunPy Sorted thus:
% No. Commits to main repo + commits in open PR's
% Date of most recent contribution
Florian Mayer$^{12}$, %721
Keith Hughitt, %446
Nabil Freij$^1$, %52
Matthew Earnshaw, %52
Tomas Meszaros$^{10}$, %17
N Chorley, %17
Samuel M Bennett$^1$, %14
M Malocha, %10
John Evans, %10 %No affil
Ankit Agrawal$^{15}$, %8
M Bates, %6
Andrew J Leonard$^7$, %3
J Ballew, %3
Thomas P Robitaille$^9$, %2
Benjamin Mampaey$^{13}$, %2
Jose Iv\'an Campos-Rozo$^{14}$ %1
and 
A Kustov %1
}

@@

$^{12}$ Vienna University of Technology, Karlsplatz 13, 1040 Vienna, Austria

$^{13}$ Royal Observatory of Belgium

$^{14}$ Observatorio Astronómico Nacional Universidad Nacional de Colombia 
Bogotá, D.C., Colombia

$^{15}$ Indian Institute of Technology, Bombay
}
